%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
% Several modifications made over original design by Justin Bass.

% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

%\usepackage{awesome-cv/awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-darknight}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{false}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
\name{}{Justin Bass}
\position{Software Engineer}
\address{1434 Whispering Trail, Irvine, CA 92602}
\mobile{949-689-8912} 

\email{justinalanbass@gmail.com}
\github{justinbass}
\linkedin{justinalanbass}
% \homepage{justinalanbass.com}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \extrainfo{extra informations}

%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Justin Bass}
  {} %{\thepage}

\cvsection{Experience}
\begin{cventries}

	\cventry
	{Software Development Engineer II} % Job title
	{Amazon.com, Inc.} % Organization
	{Irvine, CA} % Location
	{Aug 2018 - Present \textbf{}} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Lead developer for Apps and Skills linking in Appstore on Fire Tablets. Lead several developers across 4 teams to a successful delivery.}
			\item {Core developer for Alexa Voice Tips on Fire TV devices. Designed core Android controller with complex filtering conditions.}
			\item {Scrum master: mentored and coordinated team members, characterized performance, and implemented improvements.}
		\end{cvitems}
	}
	
	\cventry
	{Software Development Engineer I}
	{}
	{}
	{Nov 2016 - Aug 2018 \textbf{1.75 yrs}} {
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Lead developer for Amazon Pay integration with Appstore on Fire Tablets, lead project to successful completion.}
			\item {Core developer for 3P Developer Cards in Show Mode on Fire Tablets. Solved core technical challenges and aided project in successful delivery.}
			\item {Performed regular on-call duty, leading team members through several notable high-severity incidents quickly and effectively.}
		\end{cvitems}
	}
	
	\cventry
	{Software Engineer} % Job title
	{ViaSat Inc.} % Organization
	{Carlsbad, CA} % Location
	{Apr 2015 - Nov 2016, \textbf{1.5 yrs}} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Core programmer for Tcl test-automation framework tool, designed bindings for Python while mentoring and leading two junior team members.}
			\item {Lead team to adopt Ansible and enforced dev-ops practices for server maintenance, greatly improved reliability and reduced manual effort.}
			\item {Took up a critical past-due Python test system-monitoring project within my first 2 months, passed acceptance tests and improved testing.}
		\end{cvitems}
	}
	
	\cventry
	{Software Engineering Intern} % Job title
	{ViaSat Inc.} % Organization
	{Carlsbad, CA} % Location
	{Summer 2013, 2014, \textbf{9 mo}} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {2014: Used AWS EC2 clouds and Git to automate and expedite firewall requests and audits.}
			\item {2013: Developed tool that prevents thousands of ineffective service calls monthly.}
		\end{cvitems}
	}
	
	\cventry
	{Test Engineering Intern} % Job title
	{Conexant Systems, Inc.} % Organization
	{Newport Beach, CA} % Location
	{Aug 2011 - Feb 2013, \textbf{1.5 yrs}} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Developed C/C++ automation tools, brought intensive testing project to successful completion.}
		\end{cvitems}
	}
\end{cventries}

\cvsection{Education}
\begin{cventries}
	\cventry
	{Master of Science in Computer Science} % Degree
	{University of California, Los Angeles} % Institution
	{Los Angeles, CA} % Location
	{Sep 2013 - Mar 2015, \textbf{1.5 yrs}} % Date(s)
	{
		\begin{cvitems} % Description(s) bullet points
			\item {Bioinformatics master's project, computer vision and graphics, algorithms and theory, programming lanuages, operating system design}
		\end{cvitems}
	}
	
	\cventry
	{Bachelor of Science in Electrical Engineering} % Degree
	{University of California, Irvine} % Institution
	{Irvine, CA} % Location
	{Sep 2009 - Mar 2013, \textbf{3.5 yrs}} % Date(s)
	{
		\begin{cvitems} % Description(s) bullet points
			\item {C programming, Android game programming (Java), circuit design and analysis (Mathematica).}
		\end{cvitems}
	}
\end{cventries}

\cvsection{Skills}
\begin{cvskills}
	\cvskill
	{Great leadership ability}
	{I excel at leading and coordinating team members to successful completion of a project, and love mentoring.}
	
	\cvskill
	{Works well in a team}
	{I encourage other's professional development and am adept at conflict resolution and mediation.}

	\cvskill
	{Proficient with}
	{Kotlin, Java, Android, Python, C/C++, Tcl, Linux, Ansible, AWS Stack, OpenStack, Git, Web Stack, {\fontfamily{}\selectfont \LaTeX}\ (and vim!).}
\end{cvskills}

\end{document}
